---
title: "FENZ building fire"
author: "Christina Magill"
date: '`r Sys.Date()`'
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

Analysis was carried out using:

1.  FENZ building fire call-out data (2003 - 2022)
2.  GNS building database (2022)
3.  Census data (2018, 2013, 2006) at SA1 level

Analysis was carried out in two steps:

1.  Fire occurrence (i.e. probability of occurring in FENZ dataset)
2.  Fire severity (area of damage, percentage of building saved, casualties, fatalities, injuries)

```{r import, echo=FALSE}

buildings_fenz <- read.csv("../FENZ with building data/FENZIncidentsBuildings_new_MeshblockIDs_NZDep.csv")  # FENZ + GNS
buildings_gns <- read.csv("Buildings/Buildings_AllNZ_AllColumns.csv")   

```

## Use categories

```{r use categories, echo=FALSE}

library(ggplot2)
#library(dplyr)
#library(tidyr)

to_compare_FENZ <- subset(buildings_fenz, select = c(Use_Category,Construction_Type_1,Wall_Const,Roof_Const,Roof_Pitch,Parapet,Assign_type,Age))
to_compare_FENZ$dataset <- "FENZ"
to_compare_FENZ <- rename(to_compare_FENZ, Construction_Type="Construction_Type_1")


to_compare_GNS <- subset(buildings_gns, select = c(Use_Category,Construction_Type,Wall_Const,Roof_Const,Roof_Pitch,Parapet,Assign_type,Age))
to_compare_GNS$dataset <- "GNS"

to_compare <- bind_rows(to_compare_GNS,to_compare_FENZ)

#table(to_compare$dataset, to_compare$Use_Category)

ggplot(to_compare) +
  aes(x = dataset, fill = Use_Category) +
  geom_bar(position = "fill")



```

## Chi-square analysis building categorical data

Records with < 5 in category removed  
Records with no category recorded removed  
Parapets excluded  

```{r chi-square, echo=FALSE}

library(summarytools)
library(dplyr)
library(rmarkdown)

# Use Category
subset(to_compare, Use_Category!="" & Use_Category!="Clear Site") %$%
  ctable(Use_Category,dataset,
    prop = "c", chisq = TRUE, headings = FALSE
  ) %>%
  print(
    method = "render",
    style = "latex",
    footnote = NA
  )

subset(to_compare, Construction_Type!="") %$%
  ctable(Construction_Type, dataset,
    prop = "c", chisq = TRUE, headings = FALSE
  ) %>%
  print(
    method = "render",
    style = "rmarkdown",
    footnote = NA
  )

subset(to_compare, Wall_Const!="") %$%
  ctable(Wall_Const, dataset,
    prop = "c", chisq = TRUE, headings = FALSE
  ) %>%
  print(
    method = "render",
    style = "rmarkdown",
    footnote = NA
  )

subset(to_compare, Roof_Const!="") %$%
  ctable(Roof_Const, dataset,
    prop = "c", chisq = TRUE, headings = FALSE
  ) %>%
  print(
    method = "render",
    style = "rmarkdown",
    footnote = NA
  )

subset(to_compare, Roof_Pitch!="") %$%
  ctable(Roof_Pitch, dataset,
    prop = "c", chisq = TRUE, headings = FALSE
  ) %>%
  print(
    method = "render",
    style = "rmarkdown",
    footnote = NA
  )

#to_compare %$%
#  ctable(dataset, Parapet,
#    prop = "r", chisq = TRUE, headings = FALSE
#  ) %>%
#  print(
#    method = "render",
#    style = "rmarkdown",
#    footnote = NA
#  )

#to_compare %$%
#  ctable(dataset, Assign_type,
#    prop = "r", chisq = TRUE, headings = FALSE
#  ) %>%
#  print(
#    method = "render",
#    style = "rmarkdown",
#    footnote = NA
#  )

```




```         
  Based on categorical data, relative probability of occurrance based on building characteristics.  
  Although fire occurrance dependent on both building and demographic characterisitcs, we were only able to utilise data available for the entire country at building level. 
```

## Fire severity

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
#plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
